\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage{fullpage}
\usepackage{caption}

\minutesstyle{
	columns = {1},
	header =  {list},
	vote = {list},
	contents = {true},
}


\begin{document}

\begin{Minutes}{Davis Computer Science Club\\Officer Board Meeting}

\minutetaker{(Not Recorded)}
	
\participant{(Not Recorded)}

\missingExcused{(Not Recorded)}

\missingNoExcuse{(Not Recorded)}

\minutesdate{August 13, 2013.}

\starttime{8:24 p.m.}
\endtime{10:35 p.m.}

\location{(Not Recorded)}

\maketitle

\topic{First Meeting of Fall Quarter}

\subtopic{Last Year's First Meeting}

\begin{itemize}
	\item Booth setup: Mock interviews, UCD Mobile Project, Advisors, Resources
	\item Booths did not have follow-up content
\end{itemize}

\subtopic{General Purpose of First Meeting}

\begin{itemize}
	\item What is this meeting for?
	\item How can we focus on member retention using this first meeting?
	\item What are the priorities of our members (specifically freshmen)?
\end{itemize}

\subtopic{Possible Ideas}

\begin{itemize}
	\item Flyers (possible calendar of events, what committees do)
	\item We should get a bigger room
	\begin{itemize}
		\item Kemper lobby (difficult to organize)
	\end{itemize}
	\item Presentation as an introduction
	\item Emphasize interactivity (icebreaker)
	\item Separation of students by year or by membership status
	\item Addressing ongoing projects or present cool projects in the club
	\item Career oriented events for Juniors/Seniors and workshop directed events for Freshman/Sophomores
	\item Address administrative issues (meeting times and whatnot) and something to inspire students to stick with CS (motivational speaker --- either professor or student)
	\item Ice cream social + Oculus Rift + Leap Motion
	\item Officers should be proactive on helping students feel inclusive
\end{itemize}

\subtopic{Agenda Draft (60 minutes) @ 6:30 p.m.}

\begin{enumerate}
	\item Introductions of people and club : 10 min.
	\begin{enumerate}
		\item Who we are and why we love the club
		\item Flyers
	\end{enumerate}
	\item Upcoming Events : 5 min.
	\item Committee Introductions : 10 min.
	\item Closing Remarks : 5 min.
	\item Social : Remaining time.
\end{enumerate}

\subtopic{Marketing}

\begin{itemize}
	\item Tabling
	\item Flyers
	\item A-Frame
	\item In-class presentations / Writing on boards
	\item Lori's Undergraduate Listserv
	\item Possible website display
	\item Branding advertising materials
	\item Bainer/Kemper poster
	\item Facebook / Google Events
\end{itemize}

\topic{General Meetings}

\begin{itemize}
	\item Last year's general meeting contents were more out of necessity than for benefit
\end{itemize}

\subtopic{Club Structure}

\begin{itemize}
	\item Monthly Club Socials
	\begin{itemize}
		\item Upcoming Events
		\item Social Aspect
	\end{itemize}
	\item Ongoing Events
	\begin{itemize}
		\item Pragmatic Programming Committee
		\item Tutoring Committee
		\item Resume Workshop
	\end{itemize}
	\item Special Events
	\begin{itemize}
		\item Speakers
		\item Company Presentations
	\end{itemize}
\end{itemize}

\topic{Facebook Group Rules}

This facebook group is for sharing interesting topical news and events related to the topic of Computer Science. (Or asking for advice in UCD CS?) Any promoting of non-affiliated groups, projects, or ideas should first receive approval from one of the admins or otherwise risk removal and public humiliation

\subtopic{Violation}

\begin{enumerate}
	\item Tell other officers you're handling the post in order to avoid multiple people contacting them
	\item Contact the author of the post explaining the group rules and the reasoning for removal of post
\end{enumerate}

\subtopic{Removal Template}

Hey, (insert name here), I had to remove your post because it violated our page rules. Feel free to share that post here: (insert link to relevant page). If you have any questions, or want to work with us to publicize your (insert topic here), then let me know and I will work with you to meet our guidelines. Thanks for understanding!

\topic{Website}

Tasks were delegated for this agenda item. Please see Trello.

\end{Minutes}

\end{document}