\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage{fullpage}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{textcomp}

\minutesstyle{
  columns = {1},
  header =  {list},
  contents = {true},
}

\fancypagestyle{creditfooter}{%
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\LaTeX:\ Bryan Ngo}
\fancyfoot[C]{\thepage}
}

\begin{document}
\begin{Minutes}{Davis Computer Science Club\\Officer Board Meeting}
\minutetaker{Bryan Ngo}
\participant{%
  Corey Mason, %
  Kiran Bhadury, %
  Prajakta Surve, %
  Pranav Gupta, %
  Sam Lee, %
  Sam Tsoi, %
  Stephanie Chang, %
  Teresa Liu, %
  Trevor Glynn, %
  Pooja Rajkumar, %
  Jeffrey Warner%
}
\missingExcused{%
  Sravya Divakarla%
}

\missingNoExcuse{%
  Ariel Shin, %
  Alex Fu, %
  Michael Lee, %
  Zain Budhwani%
}

\minutesdate{March 9, 2017}

\starttime{5:09 p.m.}
\endtime{6:05 p.m.}

\location{Kemper 1066}

\maketitle

\topic{Meet the Professor Cancellation}
\begin{itemize}
    \item Classroom vists went pretty good.
    \item Natasha notified students about the cancellation of the event.
\end{itemize}

\topic{Sticker/Stoll/Banner Designs}
\begin{itemize}
    \item No designs submitted by members (Primary means of advertising: Facebook).
    \item Designs delegated to Parajakta. (Banner priority)
\end{itemize}

\topic{Cyber Security Checkin}
\begin{itemize}
    \item Will hold an event to teach members how to create code to exploit a website.
    \item This even will happen during week 2.
    \item Event name TBA
\end{itemize}

\topic{Finalize Officer Schedules}
\begin{itemize}
    \item Everyone needs to send schedules by next Wednesday (3/15/17) to Pooja.
    \item It is noted that many schedules are not solidified. Include any waitlisted classes/potential work schedule if possible.
\end{itemize}


\topic{Redefining of Officer Roles and Responsibilities}
\begin{itemize}
    \item Observation: Meetings are not high in quantity, so they are high in quality.
    \item Number of meetings an officer is allowed to miss shall be changed from 3 to 2. 
        \begin{itemize}
            \item Needs to be changed in Constitution
        \end{itemize}
    \item Missing meetings are made up by contributing n hours of work/volunteer time where n is larger than the meeting time.
        \begin{itemize}
            \item This "punishment" is easily relieved by hosting events (see Note 7)
        \end{itemize}
    \item Reinforcement of officer roles/responsibilities.
    \begin{itemize}
        \item Every officer has to help/volunteer for at least 3 events a quarter
        \item Every officer has to attend all officer meetings
        \item Every officer has to table at the beginning of the quarter
    \end{itemize}
    \item Not doing one of the listed requirements will result in a deduction of "hours"
    \item Each event should have at least 2 officers in attendance (further defined by the actual event). 
    \item New amendment to be added shall be titled "General Officer Requirements"
\end{itemize}

\topic{Intel Event Recap}
\begin{itemize}
    \item Will use Facebook event as sign in sheet.
    \item Reimbursement check has not come in yet.
\end{itemize}


\topic{Finalize Events for Spring}
\begin{itemize}
    
    \item Week 1
        \begin{itemize}
            \item General meeting will be a social with Root Beer Floats with introduction of Assassin.
            \begin{itemize}
                \item Awards to be given out to player with most kills/style points/etc.
                \item Additional logistics to be worked out at a later date. 
            \end{itemize}
            \item Mock Interview + Resume Workshop in preparation for Spring Career Fair
        \end {itemize}
    
    \item Week 2
        \begin{itemize}
            \item Meet the tutors
            \item Coders Conundrum (aka brain teasers)
        \end{itemize}

    \item Week 3 
        \begin{itemize}
            \item Code in the Dark Hackathon
        \end{itemize}

    \item Week 4
        \begin{itemize}
            \item Algorithm Hackathon
        \end{itemize}

    \item Week 5
    \begin{itemize}
        \item Student Panel + Classes Preview
        \item Elections
    \end{itemize}

    \item Week 6
    \begin{itemize}
        \item Meet the Professor 
        \item Gender Diversity
    \end{itemize}

    \item Week 7
    \begin{itemize}
        \item Alumni Panel 
        \item Banquet (on Saturday)
    \end{itemize}

    \item Week 8
    \begin{itemize}
        \item Love 2D Workshop
    \end{itemize}

    \item Week 9
    \begin{itemize}
        \item Destresser
    \end{itemize}
    
    \item Additional information about all these events (host, number of officers needed, etc) can be found in the Google Drive. Filename = "Spring Quarter Ideas"
\end{itemize}


\topic{Misc}
\begin{itemize}
    \item Possibility for officers to get units
        \begin{itemize}
            \item Still checking this with Natasha.
        \end{itemize}
    \item Officer of the year awards.
        \begin{itemize}
            \item Gift cards?
            \item Pull funds from account/donations from club officers.
        \end{itemize}
\end{itemize}

\thispagestyle{creditfooter}

\end{Minutes}

\end{document}