\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage{fullpage}
\usepackage{caption}

\minutesstyle{
	columns = {1},
	header =  {list},
	vote = {list},
	contents = {true},
}


\begin{document}

\begin{Minutes}{Davis Computer Science Club\\Officer Board Meeting}

\minutetaker{Iris Chan}
	
\participant{Alberto Salazar, Alexander Parella, Betty Leung, Calvin Li, Christina Zhu, Christine Franks, Jacob Brownlee, Iris Chan, Joanne Arboleda, Karen Chan, Kelvin Lu, Michael Lee, Pouneh Aghababazadeh, Raymond Chan, Russell Miller, Rylan Schaeffer, Samuel Lin, Shyam Pinnipati, Timothy Tong, Trevor Glynn}

\missingExcused{Conrad Fay, Yvone Chau}

\missingNoExcuse{Felix Borovikov, Jackie Zhang, Michael Lu}

\minutesdate{March 30, 2015.}

\starttime{6:10 p.m.}
\endtime{7:13 p.m.}

\location{Kemper 1131}

\maketitle

\topic{Bylaw Amendments}
	
\begin{Vote}
	\vote{Board Approval}{16}{0}{3}[Approved]
\end{Vote}
	
\topic{Spring Kickoff}

Held in Giedt 1003 starting from 6:30 p.m. Slides will contain:

\begin{enumerate}
	\item Title Slide
	\item Bylaw Ratification
	\item Election Details
	\item Upcoming Events
\end{enumerate}

\topic{Elections}

\begin{itemize}
	\item Held in Kemper 1127/1131 from 6:00 p.m. to 7:00 p.m. on April 8. 
	\item Use a timer on laptop to display remaining time.
	\begin{itemize}
		\item Combine Q \& A time with speech time.
		\item 5 minutes in total.
	\end{itemize}
	\item Count votes by paper.
	\item Have a representative for candidates who cannot attend.
	\item Provide results to runner-ups only when asked.
\end{itemize}

\topic{Feedback Review}

\begin{itemize}
	\item Majority of members discover events or club through Facebook.
	\item Primary interests in club
	\begin{enumerate}
		\item Social Aspects
		\item Academic
		\item Tutoring
	\end{enumerate}
	\item High interests in socials, web development, and app development.
	\item Need a consistent organized place for events.
\end{itemize}

\topic{Committee Plans}

\subtopic{Game Development}

Picnic Day

\subtopic{Pragmatic Programming}

LA Hack, App Development

\subtopic{Professional Development}

Chair and Vice-Chair Missing. 

\subtopic{Tutoring}

Continue tutoring and review sessions.

\subtopic{Web Development}

Need to focus on the website. Team wants to do workshops, but lacking brain/manpower. Potentially recruiting members to help.

\topic{DevHub}

Space for people to come out and work on their own projects. Similarly to how Game Dev. committee runs. Potentially hold talks and workshops occasionally.

\topic{Spring Quarter Events}

\begin{table}[h]
	\centering
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{l l c}
		Event
			&	Leads
			&	Date\\
		\hline
		April General Meeting
			&	Timothy Tong
			&	April 1\\
		Elections
			&	Timothy Tong
			&	April 8\\
		Cultive Fundraiser
			&	Joanne Arboleda
			&	April 8\\
		4th Grade Presentation	
			&	Raymond Chan
			&	April 15\\
		Picnic Day
			&	Conrad Fay
			&	April 18\\
		Dot Island Grill Fundraiser
			&	Joanne Arboleda
			&	April 22\\
		May General Meeting
			&	TBD
			&	May 6\\
		Dot Island Grill Fundraiser
			&	Joanne Arboleda
			&	May 9\\
		Gender Diversity	
			&	Betty Leung, Joanne Arboleda	
			&	Late May\\
		Banquet
			&	Iris Chan
			&	TBA\\
		Byte/Bit Socials
			& 	Iris Chan
			&	TBA\\
		Coder's Conundrum	
			&	Timothy Tong	
			&	TBA\\
		Crash Course
			&	Raymond Chan
			&	TBA\\
		De-Stresser
			&	TBD
			&	TBA\\
		Fundraisers
			&	Joanne Arboleda
			& 	TBA\\
		GDB Workshop		
			&	Russell Miller	
			&	TBA\\
		Social with Professors
			&	Rylan Schaeffer
			&	TBA\\
		Next Quarter Classes Preview
			&	Pouneh Aghababazadeh
			&	TBA\\
		Smash Tournament	
			&	Christina Zhu, Iris Cha, Michael Lee
			&	TBA\\
	\end{tabular}
	\caption*{Excludes committee events}
\end{table}


\end{Minutes}

\end{document}