\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage{fullpage}
\usepackage{caption}
\usepackage{float}

\minutesstyle{
	columns = {1},
	header =  {list},
	vote = {list},
	contents = {true},
}


\begin{document}

\begin{Minutes}{Davis Computer Science Club\\Officer Board Meeting}

\minutetaker{Iris Chan}
	
\participant{Aedi Wang, Alexander Parella, Calvin Li, Christina Zhu, Christy Franks, Jacob Brownlee, Jackie Zhang, Joanne Arboleda, Kelvin Lu, Laila Rizvi, Michael Lee, Pouneh Aghababazadeh, Raymond Chan, Russell Miller, Samuel Lin, Stefan Peterson, Stephanie Chang, Timothy Tong, Yvone Chau}

\missingExcused{Arjun Bharadwaj, Betty Leung, Mariah Arevalo, Shyam Pinnipati}

\missingNoExcuse{Conrad Fay, Felix Borovikov, Michael Lu}

\minutesdate{April 15, 2015.}

\starttime{6:16 p.m.}
\endtime{6:56 p.m.}

\location{Kemper 1131}

\maketitle

\topic{Welcome Newly Elected Officers}
	
\begin{itemize}
	\item Yvone Chau, \textit{President}
	\item Aedi Wang, \textit{Vice-President of Internal Affairs}
	\item Mariah Arevalo, \textit{Vice-President of External Affairs}
	\item Jacob Brownlee, \textit{Treasurer}
	\item Stephanie Chang, \textit{Secretary}
	\item Christina Zhu, \textit{Marketing Director}
	\item Michael Lee, \textit{Game Development Chair}
	\item Arjun Bharadwaj, \textit{Pragmatic Programing Chair}
	\item Laila Rizvi, \textit{Professional Development Chair}
	\item Alexander Parella, \textit{Tutoring Committee Co-Chair}
	\item Shyam Pinnipati, \textit{Tutoring Committee Co-Chair}
	\item Kelvin Lu, \textit{Web Development Chair}
\end{itemize}	

Terms for the newly elected officers do not officially begin until the last academic day of Spring Quarter 2015. All newly elected officers will shadow the current officers to learn the internal workings of the club. The newly elected officers will plan and run the De-Stresser event with support from the current officer board.

\topic{Events Coordinator}

No one ran for events coordinator during elections. The task of finding and choosing the new events coordinator is at the discretion of the newly elected officer board.

\topic{Outreach: Teaching Fourth Graders}

Very successful event. Taught Scratch to fourth graders. Looking to host this as an annual event.

\topic{Smash Tournament}

May 23 (Saturday)\\
Lead: Iris Chan\\

Can ask Smash Club to help out again.

\topic{Gender Diversity in Technology}

May 13 (Wednesday)\\
6:00 p.m. - 9:00 p.m.\\
Giedt 1003\\
Leads: Betty Leung, Joanne Arboleda, Stephanie Chang

\begin{itemize}
	\item 3 Keynote speakers
	\begin{itemize}
		\item 1 responded with no already
		\item Waiting on other two (So Choi and Charlyn Gonda)
	\end{itemize}
\end{itemize}

\topic{Coder's Conundrum}

Date Unknown\\
Time Unknown\\
Location Unknown\\
Leads: Alexander Parella, Calvin Li, Timothy Tong\\

\begin{itemize}
	\item Reaching outside of leadership board for help
	\item Compiling list of puzzles.
\end{itemize}

\topic{Banquet}

Lead: Iris Chan

\begin{itemize}
	\item Looking at venues
	\item Working on budget
	\item Last year's budget was approximately \$1000
\end{itemize}

\topic{DevHub}

Lead: Pouneh Aghabazadeh

\begin{itemize}
	\item Continuing with current process
	\item Pebble can help with DevHub in Fall Quarter 2015
\end{itemize}

\topic{Committee Checkup}

\subtopic{Game Development}

\begin{itemize}
	\item Game Jam
	\begin{itemize}
		\item May 25 (Saturday)
		\item Chipotle and Krispy Kreme sponsorship
	\end{itemize}
\end{itemize}

\subtopic{Pragmatic Programming}

\begin{itemize}
	\item Git Tutorial was a success
	\item No meeting nor room this coming week
	\item Christy Franks is offering to take over events
\end{itemize}

\subtopic{Professional Development}

\begin{itemize}
	\item Passing events to Rylan Schaeffer
\end{itemize}

\subtopic{Tutoring Committee}

\begin{itemize}
	\item No review sessions yet.
\end{itemize}

\subtopic{Web Development}

\begin{itemize}
	\item Passing website off to Kelvin
	\item No events this quarter
	\item Hoping to host workshops in Fall
\end{itemize}

\topic{Spring Quarter Events}

\begin{table}[h]
	\centering
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{l l c}
		Event
			&	Leads
			&	Date\\
		\hline
		Picnic Day
			&	Conrad Fay
			&	April 18\\
		May General Meeting
			&	Officers
			&	May 6\\
		Dot Island Grill Fundraiser
			&	Joanne Arboleda
			&	May 9\\
		Gender Diversity	
			&	Betty Leung, Joanne Arboleda	
			&	May 13\\
		Banquet
			&	Iris Chan
			&	May 30\\
		Byte/Bit Socials
			& 	Iris Chan
			&	TBA\\
		Coder's Conundrum	
			&	Timothy Tong	
			&	TBA\\
		Crash Course
			&	Raymond Chan
			&	TBA\\
		De-Stresser
			&	TBD
			&	TBA\\
		GDB Workshop		
			&	Russell Miller	
			&	TBA\\
		Next Quarter Classes Preview
			&	Pouneh Aghababazadeh
			&	TBA\\
		Smash Tournament	
			&	Christina Zhu, Iris Chan, Michael Lee
			&	TBA\\
	\end{tabular}
	\caption*{Excludes committee events}
\end{table}


\end{Minutes}

\end{document}