\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage{fullpage}
\usepackage{caption}

\minutesstyle{
	columns = {1},
	header =  {list},
	vote = {list},
	contents = {true},
}


\begin{document}

\begin{Minutes}{Davis Computer Science Club\\Officer Board Meeting}

\minutetaker{Iris Chan}
	
\participant{Aedi, Alex Parella, Betty Leung, Calvin Li, Christy Franks, Ezequiel, Iris Chan, Jackie Zhang, Jake Brownlee, Karen, Layla, Mariah, Phuong Nguyen, Pouneh Aghababazadeh, Raymond Chan, Russell Miller, Shyam Pinnipati, Stefan Peterson, Stephanie, Timothy Tong, Vivian}

\missingExcused{Alberto Salazar, Conrad Fay, Joanne Arboleda, Kelvin Lu, Samuel Lin, Yvone Chau}

\missingNoExcuse{Felix Borovikov, Michael Lu}

\minutesdate{April 6, 2015.}

\starttime{6:10 p.m.}
\endtime{7:00 p.m.}

\location{Kemper 1131}

\maketitle

\topic{Elections}
	
April 8 (Wednesday)\\
00:00 p.m. - 00:00 p.m.\\
Kemper 1127/1131	

\begin{itemize}
	\item Two minute speeches
	\item Two questions from officers of that position
	\item Questions addressed to all candidates
	\item 30 seconds to answer questions
\end{itemize}
	
\topic{Decision Day Tabling}

April 11 (Saturday)\\
Volunteers: Iris Chan, Calvin Li, Pouneh Aghababazadeh

\begin{itemize}
	\item Students will ask questions about computer science and/or CS Club
	\item Wear club t-shirts
	\item Decorate table
	\item Bring laptop to show list of events the CS Club has held
	\item Use as an opportunity to advertise the club
\end{itemize}

\topic{Teaching Fourth Grade}

Lead: Raymond Chan\\
Volunteers: Aedi, Mariah, Pouneh Aghababazadeh\\
April 15\\

\task{April 8}{Finish preparing material}

\topic{DevHub}

Lead: Pouneh Aghababazadeh

\begin{itemize}
	\item First meeting on April 7 (Tuesday)
	\item Wellman 234
	\item 7:30 p.m.
\end{itemize}

\topic{Competitive Programming}

Host of competitive programming was absent.

\topic{Smash Tournament}

Lead(s): Iris Chan, Shyam Pinnipati\\

\task{Contact Joanne to see how she ran the tournament}

\topic{Gender Diversity}

Lead(s): Betty Leung, Joanne Arboleda\\

\task{April 7}{First planning meeting}
\task{}{Apply for potential diversity grants}

\topic{Coder's Conundrum}

Lead: Timothy Tong\\
Volunteer(s): Alex Parella, Calvin Li, Michael Lee, Romer Ibo (Alumni)\\

\task{}{First collaboration meeting this week}

\topic{Bit/Byte Program}

No plans at the moment.

\topic{Banquet}

\begin{itemize}
	\item Tentative date: May 30
	\item Questions:
	\begin{itemize}
		\item What is our budget?
		\item What is our venue?
		\begin{itemize}
			\item Kemper?
			\item Sudwerks?
		\end{itemize}
		\item Do we charge a slight fee?
	\end{itemize}
	\item Semi-formal attire
\end{itemize}

\topic{Committee Checkup}

\subtopic{Game Development}

\begin{itemize}
	\item Working with Josef Nguyen on workshops
	\item Electing the new committee chair this week
\end{itemize}

\subtopic{Pragmatic Programming}

\begin{itemize}
	\item Chair needs to catch up on work
	\item Perhaps host a hangout where people can just work on stuff
	\item Potentially a basic Git tutorial
\end{itemize}

\subtopic{Professional Development}

Resume workshop

\subtopic{Tutoring}

Continue tutoring and review sessions. Almost 40 tutors.

\subtopic{Web Development}

Chair and vice-chair missing.

\topic{Misc}

\subtopic{D2}

\begin{itemize}
	\item Davis only
	\item Pebble is sponsoring
	\item Need to check legality on Pebble selling discounted items on campus
\end{itemize}

\subtopic{Meeting with Professors}

Professors to check with: Dipak Ghosal, Felix Wu, Matthew Farrens, Phillip Rogaway, Ronald Olsson

\subtopic{Outreach Program}

\begin{itemize}
	\item Meeting with freshmen/sophomore
	\item Teaching fourth graders is one example
\end{itemize}

In light of this, the Social/Outreach Committee will be undergoing a trial period for Spring Quarter 2015. Iris Chan, Ezequiel, Mariah, and Raymond Chan will be overseeing this program. The committee will be reviewed at the end of the quarter.

\subtopic{Fundraising Committee}

Creating a fundraising committee to offload some of the weight from the Marketing Director. Formation begins after the 2015 elections.

\topic{Spring Quarter Events}

\begin{table}[h]
	\centering
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{l l c}
		Event
			&	Leads
			&	Date\\
		\hline
		DevHub
			&	Pouneh Aghababazadeh
			&	April 7\\
		Elections
			&	Officers
			&	April 8\\
		Decision Day Display
			&	Iris Chan, Calvin Li, Pouneh Aghababazadeh
			&	April 11\\
		4th Grade Presentation	
			&	Raymond Chan
			&	April 15\\
		Picnic Day
			&	Conrad Fay
			&	April 18\\
		Dot Island Grill Fundraiser
			&	Joanne Arboleda
			&	April 22\\
		May General Meeting
			&	Officers
			&	May 6\\
		Dot Island Grill Fundraiser
			&	Joanne Arboleda
			&	May 9\\
		Gender Diversity	
			&	Betty Leung, Joanne Arboleda	
			&	Late May\\
		Banquet
			&	Iris Chan
			&	May 30\\
		Byte/Bit Socials
			& 	Iris Chan
			&	TBA\\
		Coder's Conundrum	
			&	Timothy Tong	
			&	TBA\\
		Crash Course
			&	Raymond Chan
			&	TBA\\
		De-Stresser
			&	TBD
			&	TBA\\
		Fundraisers
			&	Joanne Arboleda
			& 	TBA\\
		GDB Workshop		
			&	Russell Miller	
			&	TBA\\
		Social with Professors
			&	Rylan Schaeffer
			&	TBA\\
		Next Quarter Classes Preview
			&	Pouneh Aghababazadeh
			&	TBA\\
		Smash Tournament	
			&	Christina Zhu, Iris Chan, Michael Lee
			&	TBA\\
	\end{tabular}
	\caption*{Excludes committee events}
\end{table}


\end{Minutes}

\end{document}