\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage{fullpage}
\usepackage{caption}
\usepackage{float}

\minutesstyle{
	columns = {1},
	header =  {list},
	vote = {list},
	contents = {true},
}


\begin{document}

\begin{Minutes}{Davis Computer Science Club\\Officer Board Meeting}

\minutetaker{Stephanie Chang}

	
\participant{Aedi Wang, Alexander Parella, Arjun Bharadwaj, Betty Leung, Calvin Li, Christina Zhu, Christy Franks, Iris Chan, Joanne Arboleda, Kelvin Lu, Pouneh Aghabazadeh, Russell Miller, Samuel Lin, Shyam Pinnipati, Stephanie Chang, Timothy Tong, Yvone Chau}

\missingExcused{Conrad Fay, Laila Rizvi, Mariah Arevalo, Michael Lu, Raymond Chan}

\missingNoExcuse{Alberto Salazar, Felix Borovikov, Jackie Zhang, Jacob Brownlee, Michael Lee}

\minutesdate{April 29, 2015.}

\starttime{6:25 p.m.}
\endtime{6:52 p.m.}

\location{Giedt 1006}

\maketitle

\topic{Pebble Workshop}

May 2 (Saturday)\\
Time Unknown\\
Lead: Christy Franks\\
Location Unknown

\begin{itemize}
	\item Pebble has not responded, only two days remaining to advertise.
	\item Venue is not confirmed either.
	\item Priority is to postpone the event to a more prepared time slot.
\end{itemize}

\topic{Outreach}

Lead: Mariah Arevalo\\\\
Not present. Unable to move forward without further information and discussion.

\topic{Events Coordinator}

\begin{itemize}
	\item Last candidate is being interviewed this Friday.
\end{itemize}

\topic{May General Meeting}

May 6\\
Time Unknown\\
Location Unknown\\
Lead: Timothy Tong, Yvone Chau

\begin{itemize}
	\item Ice Breaker -- Telephone Pictionary.
	\item Selling CS Club T-Shirts.
	\item Collides with officer meeting time; therefore, no officer meetings next week.
\end{itemize}

\topic{Gender Diversity in Technology}

May 13 (Wednesday)\\
6:00 p.m. - 9:00 p.m.\\
Giedt 1002\\
Leads: Betty Leung, Joanne Arboleda, Stephanie Chang

\begin{itemize}
	\item Submitted all grants except for College of Engineering.
	\item Looking for more panelists.
\end{itemize}

\topic{Banquet}

May 30 (Saturday)\\
Lead: Iris Chan\\

\begin{itemize}
	\item Banquet Document Link: (undisclosed)
	\item Food estimates are nearing \$1000.
	\item Will work with Pouneh to investigate venues through CEVS.
	\item Will finalize pricings by next week.
	\item Potentially charge a \$ admission fee to mitigate costs.
\end{itemize}

\subtopic{On-Campus Venues}

\begin{table}[h]
	\setlength{\tabcolsep}{20pt}
	\renewcommand{\arraystretch}{1.5}
	\centering
	\begin{tabular}{| l | r |}
		\hline
		Venue
			&	Pricing\\
		\hline
		ARC	Ballroom
			&	Booked\\
		\hline
		Alumni \& Visitor Center
			&	\$152\\
		\hline
		COHO
			&	\$112\\
		\hline
		Mondavi Center
			&	\$180\\
		\hline
		Memorial Union
			&	\$126\\
		\hline
		Conference Center Ballroom A \& B
			&	\$184\\
		\hline
		Conference Center Ballroom B \& C
			&	\$184\\
		\hline
		Kemper Lobby
			&	\$0\\
		\hline
	\end{tabular}
\end{table}

\subtopic{Catering Options}

\begin{itemize}
	\item KetMoRee
	\item Panera
	\item Whole Foods
	\item Dos Coyotes
	\item Nugget
	\item Panda Express
	\item Pluto's
\end{itemize}

\subtopic{Photobooth}

\begin{itemize}
	\item Have a DSLR + Background + Props.
	\item Officers take shifts taking pictures.
\end{itemize}


\topic{Coder's Conundrum}

May 18 (Monday)\\
Time Unknown\\
Location Unknown\\
Leads: Alexander Parella, Calvin Li, Christy Franks, Michael Nam Lee, Romer Ibo, Timothy Tong\\

\begin{itemize}
	\item 10 Puzzles Total
	\item 2 Puzzles Completed
	\item Need to work on the web application for people to compete on.
\end{itemize}

\topic{Crash Course}

May 5 (Tuesday)\\
7:30 p.m. - 9:00 p.m.\\
Kemper 1065\\
Lead: Alexander Parella, Shyam Pinnipati

\begin{itemize}
	\item Time was pushed back to 7:30 p.m.
	\item ECS 124: Bioinformatics
	\item ECS 160: Software Engineering
	\item ECS 171: Macine Learning
	\item ECS 175: Computer Graphics
\end{itemize}

\topic{Next Quarter Classes Preview}

May 8 (Friday)\\
Time Unknown\\
Location Unknown\\
Lead: Pouneh Aghababazadeh

\begin{itemize}
	\item Need a room
	\item All officers must attend
\end{itemize}

\topic{DevHub}

Lead: Pouneh Aghababazadeh

\begin{itemize}
	\item Canceled this week.
	\item Colliding with a few events next week; will need to move to either next Monday or Friday.
\end{itemize}

\topic{Committee Checkup}

\subtopic{Game Development}

No representative present.

\subtopic{Pragmatic Programming}

\begin{itemize}
	\item No pragmatic programming meeting this week.
\end{itemize}

\subtopic{Professional Development}

No representative present.

\subtopic{Tutoring Committee}

\begin{itemize}
	\item ECS 60 Review - Room Reserved
	\item ECS 154B Review - Room Reserved
\end{itemize}

\subtopic{Web Development}

\begin{itemize}
	\item Must be continuously updated.
	\item Officer Bios.
	\item Sponsors need to be able to use our website.
\end{itemize}

\topic{Spring Quarter Events}

\begin{table}[h]
	\centering
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{l l c}
		Event
			&	Leads
			&	Date\\
		\hline
		Game Jam
			&	Michael Lee
			&	May 2\\
		ECS 60 Review Session
			&	Michael Lu
			&	May 4\\
		Crash Course
			&	Alexander Parella, Shyam Pinnipati
			&	May 5\\
		May General Meeting
			&	Timothy Tong, Yvone Chau
			&	May 6\\
		Dot Island Grill Fundraiser
			&	Joanne Arboleda
			&	May 6\\
		\LaTeX Tutorial
			&	Calvin Li
			&	May 7\\
		Next Quarter Classes Preview
			&	Pouneh Aghababazadeh
			&	May 8\\
		Gender Diversity	
			&	Betty Leung, Joanne Arboleda, Stephanie Chang
			&	May 13\\
		GDB Tutorial
			&	Michael Lu
			&	May 14\\
		Coder's Conundrum	
			&	Alexander Parella, Calvin Li, Christy Franks, Timothy Tong
			&	May 18\\
		Hacker's Toolbox
			&	Alexander Parella, Calvin Li, Christy Franks, Joseph McGee
			&	May 21\\
		Hacker's Toolbox
			&	Alexander Parella, Calvin Li, Christy Franks, Joseph McGee
			&	May 23\\
		Banquet
			&	Iris Chan
			&	May 30\\
		De-Stresser
			&	TBD
			&	TBA\\
	\end{tabular}
	\caption*{Excludes committee meetings}
\end{table}


\end{Minutes}

\end{document}