\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage{fullpage}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{textcomp}

\minutesstyle{
  columns = {1},
  header =  {list},
  contents = {true},
}

\fancypagestyle{creditfooter}{%
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\LaTeX:\ Bryan Ngo}
\fancyfoot[C]{\thepage}
}

\begin{document}
\begin{Minutes}{Davis Computer Science Club\\Officer Board Meeting}
\minutetaker{Bryan Ngo}
\participant{%
  Sam Lee, %
  Bryan Ngo, %
  Sam Tsoi, %
  Prajakta Surve, %
  Pranav Gupta, %
  Sravya Divakarla, %
  Pooja Rajkumar, %
  Teresa Liu, %
  Zain Budhwani %
%
}

\missingExcused{%
}

\missingNoExcuse{%
  Corey Mason, %
  Ariel Shin, %
  Alex Fu, %
  Kiran Bhadury, %
  Stephanie Chang, %
  Jeffrey Warner %
}

\minutesdate{May 1, 2017}

\starttime{7:40 p.m.}
\endtime{9:00 p.m.}

\location{Roessler 66}

\maketitle

\topic{Clean out Basement}
\begin{itemize}
    \item We need to clean out our inventory at some time. 
\end{itemize}

\topic{Bylaws Revision}
\begin{itemize}
    \item Board revisions.
    \begin{itemize}
    		\item Positions to remove include: External VP, Marketing Director, and Events Coordinator
    		\item All committees will be condensed to a "Development Committee" led by the Development Director.
    		\item Thus, the following positions for the club are updated to be: President, Vice President, Secretary, Design Director, Treasurer, Development Director, Technology Director.
    \end{itemize}
   	\item Officers should be elected at some time  during spring quarter, not by the $3^{rd}$ week of Spring quarter
\end{itemize}

\topic{Classes Preview}
\begin{itemize}
    \item We would go through all of the classes going to be offered
    \item We need ~5 people for the panel. (Pooja, Stephanie, and Pooja's friends)
    \item Each person on the panel will represent a different track. i.e. SWE, AI, etc.   	
\end{itemize}

\topic{Bit/Byte}
\begin{itemize}
    \item Pooja will conduct the rest of the events for Bit/Byte to see how it goes.
    \item Next year's board will take the Bit/Byte program in the direction they please based on the results of this quarter.
\end{itemize}

\topic{Gender Diversity in Tech}
\begin{itemize}
    \item Next meeting, we will open up a committee for putting on this event. 
\end{itemize}

\topic{Stoles}
\begin{itemize}
    \item Generally, a lot of people want stoles. 
    \item Emails have been sent out to admin about getting them.
\end{itemize}

\topic{Addendum}
\begin{itemize}
	\item Pragmatic Programming has been added back as a position.
	\item Therefore, the positions for the 2017-2018 DCSC board are President, Vice President, Secretary, Design Director, Treasurer, Pragmatic Programming, Professional Development, and Technology Director.
\end{itemize}
\thispagestyle{creditfooter}

\end{Minutes}

\end{document}
