\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage{fullpage}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{textcomp}

\minutesstyle{
  columns = {1},
  header =  {list},
  contents = {true},
}

\fancypagestyle{creditfooter}{%
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\LaTeX:\ Bryan Ngo}
\fancyfoot[C]{\thepage}
}

\begin{document}
\begin{Minutes}{Davis Computer Science Club\\Officer Board Meeting}
\minutetaker{Bryan Ngo}
\participant{%
  Bryan Ngo, %
  Prajakta Surve, %
  Pooja Rajkumar, %
  Teresa Liu, %
  Sam Tsoi, %    
  Zain Budhwani, %
  Andrew Cope, %
  Jeffrey Warner, %  
  Kiran Bhadury, %
  Corey Mason, %  
  Stephanie Chang, %
  Nikita Andrikanis, %
%
}

\missingExcused{%
}

\missingNoExcuse{%
  Sam Lee, %
  Ariel Shin, %
  Alex Fu, %
  Sravya Divakarla, %
  Pranav Gupta, %  
  Alisha Nanda, %
}

\minutesdate{May 29, 2017}

\starttime{7:30 p.m.}
\endtime{8:30 p.m.}

\location{Kemper Lobby}

\maketitle

\topic{Reimbursement Process Overview}
\begin{itemize}
	\item More than \$50, whole board must agree on spending
	\item 2 weeks before the event, Treasurer will email Natasha, after the event, forms (flyers, sign-in sheets)
	\item Less than \$50 is when it get a little more complicated (see treasurey forms for more detailed procedure).
\end{itemize}

\topic{Funding}
\begin{itemize}
	\item 2017 - 2018 year will start with 2k of funding. 
\end{itemize}

\topic{Stoles}
\begin{itemize}
	\item Stoles are bought on pre-orders; so no money should really come out of our account.
	\item Officer discount?
	\item We should have a quote by tomorrow.
\end{itemize}

\topic{Last Event}
\begin{itemize}
	\item De-stresser. Streaming Silicon Valley HBO, ice cream, pizza.
\end{itemize}

\topic{Bylaws Amendment}
\begin{itemize}
	\item Change CS club advisor from any professor to any faculty.
\end{itemize}

\thispagestyle{creditfooter}

\end{Minutes}

\end{document}
