\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage{fullpage}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{textcomp}

\minutesstyle{
  columns = {1},
  header =  {list},
  contents = {true},
}

\fancypagestyle{creditfooter}{%
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\LaTeX:\ Bryan Ngo}
\fancyfoot[C]{\thepage}
}

\begin{document}
\begin{Minutes}{Davis Computer Science Club\\Officer Board Meeting}
\minutetaker{Bryan Ngo}
\participant{%
  Bryan Ngo, %
  Sam Tsoi, %
  Prajakta Surve, %
  Pranav Gupta, %
  Sravya Divakarla, %
  Pooja Rajkumar, %
  Teresa Liu, %
  Corey Mason, %
  Zain Budhwani, %
  Jeffrey Warner, %
%
}

\missingExcused{%
}

\missingNoExcuse{%
  Sam Lee, %
  Ariel Shin, %
  Alex Fu, %
  Kiran Bhadury, %
  Stephanie Chang %
}

\minutesdate{May 8, 2017}

\starttime{7:30 p.m.}
\endtime{9:00 p.m.}

\location{Kemper 1066}

\maketitle

\topic{Banquet}
\begin{itemize}
    \item Members will be charged \$5 and Non-Members would be charge \$7
    \item We have tables already
    \item Potential themes
    \begin{itemize}
    		\item Carnival Theme 
    \end{itemize}
    \item Things to do at banquet?
    	\begin{itemize}
    		\item Large Jenga
    		\item Murder Mystery/Escape Room
    		\item Photobooth (definite yes for this)
    		\item Bounce House?
    		\item VR Carnival Experience
    	\end{itemize}
    	\item Food Options
    	\begin{itemize}
    		\item Chipotle
    	\end{itemize}
\end{itemize}

\topic{This Thursday's Event}
\begin{itemize}
    \item Possible change to Meet the Professor for Rob.
\end{itemize}

\topic{Stoles}
\begin{itemize}
    \item Only club members, current graduating officers, and previous graduating officers.
	\item Only club members get club stoles. CS stoles are to be sold separately.
\end{itemize}

\topic{Position Redefining}
\begin{itemize}
    \item Design Director:
    \begin{itemize}
    		\item Designs graphics, banners, T-Shirts, stickers, stoles for club branding.
    \end{itemize}
    \item Technology Director:
    \begin{itemize}
    		\item Manage Facebook
    		\item Manage website
    		\item Answers all relevant emails
    		\item Manages Social Media
    \end{itemize}
   	
   	\item Changes/modifications for these positions have been unanimously approved by the board. 
\end{itemize}

\topic{Elections}
\begin{itemize}
    \item Candidates would only need to present their reasoning for running.
    \item Candidates are able to run up to 3 positions
    \item Officers pick the top three people for each positions
    \item Each position will consist of 4 general position, and one specific question to the position.
    \begin{itemize}
    		\item i.e. Design Director would need to provide some sort of portfolio. 
    \end{itemize}
\end{itemize}

\thispagestyle{creditfooter}

\end{Minutes}

\end{document}
