\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage{fullpage}
\usepackage{caption}
\usepackage{fancyhdr}


\minutesstyle{
	columns = {1},
	header =  {list},
	contents = {true},
}

\fancypagestyle{creditfooter}{%
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\LaTeX:\ Trevor Glynn}
\fancyfoot[C]{\thepage}
}

\begin{document}
\begin{Minutes}{Davis Computer Science Club\\Officer Board Meeting}
\minutetaker{Trevor Glynn}
\participant{Alex Fu, Ariel Shin, Pooja Rajkumar, Prajakta Surve, Pranav
Gupta, Russell Miller, Sravya Divakrla, Stephanie Chang, Teresa Liu,
Trevor Glynn, Zane Budhwani}
\missingExcused{Sam Tsoi}
\missingNoExcuse{}

\minutesdate{May 25, 2016}

\starttime{4:01 p.m.}
\endtime{5:04 p.m.}

\location{Kemper 1066}

\maketitle
\topic{Destresser}
\begin{itemize}
\item Have GameCube, SSBM, and CRT
\item Need GameCube controllers
\item CAH, cards, board games
\item \textbf{May want to buy GameCube controllers for Smash tournament in FQ}
\item Use Netflix or Redbox for movies
\item Need cups, hot water, pitcher, ice, etc.
\item Cups are in downstairs storage
\item Field trip to storage after the meeting
\item Will distribute t-shirts
\item Put event up on Facebook
\end{itemize}

\topic{Communications}
\begin{itemize}
\item Some members don't want to use Slack, prefer Facebook
\item Use Google Calendar for events?
\item \textbf{Use a generic DCSC Facebook user account for official business}
\item Make only the generic account an admin on the page
\item Make everyone else an unprivileged user
\end{itemize}

\topic{Plans for next year}

\subtopic{Recruiting events}
\begin{itemize}
\item Promote each recruiting event on Facebook
\item Send a board member to each of these events
\item Encourage recruiting event organizers to come back
\end{itemize}

\subtopic{Fall welcome}
\begin{itemize}
\item Hand out pamphlets in fall (esp. first two weeks)
\item More active promotion of club events
\item Make club look less intimidating to freshmen (mock interviews, \dots)
\item Focus on vices (\textit{interns?}) for board members
\item Start tabling around the DC
\item Get more money to spend on promoting the club
\item Do more \textit{low-key} tutoring promotion
\end{itemize}

\subtopic{Dues and other fundraising ideas}
\begin{itemize}
\item Pros: funding, incentive for paying members to attend events
\item Cons: discouraging new members
\item \textit{Keep tutoring free for all}
\item Five dollars
\item Members should \textit{get something back} for dues
\item Choice between upfront membership fee or event fees
\item Waive fee after attending enough events (3)?
\item Offer discounts on t-shirts (we're making a 200\% profit right now)
\item Offer stickers (GitHub?)
\item Maybe add a cost to Smash tournament
\item How to enforce?  Should we?
\item What about people who attend just one or two events?
\item Membership card (digital)?
\item \textbf{Solicit member feedback for all of this}
\item Ask for sponsorships/donations
\item Get EIN
\end{itemize}
\thispagestyle{creditfooter}
\end{Minutes}
\end{document}
